Data_cleaning

### 2021-06-22 1_cleaning.Rmd
update

ind <-
  read.dta13("1_country_data/ind/IGC_vacstudy_blfu12.dta", 
             nonint.factors = TRUE) %>%
  dplyr::as_tibble() %>% 
  dplyr::filter(!is.na(vac1)) %>% 
  dplyr::rename(
    age = HH_age,
    gender = HH_sex,
    take_vaccine = vac1) %>%
  dplyr::mutate(
    study = "ind_igc",
    educ = ifelse(hhb_hh_head_educs == 1, "More than secondary", NA_character_),
    educ = ifelse(hhb_hh_head_educs == 0, "Less than secondary", educ),
    gender = as.factor(gender),
    gender = recode(gender, 
                    "1" = "Male", 
                    "0" = "Female"), 
    take_vaccine = recode(take_vaccine, 
                          "Yes, only for free" = "Yes", 
                          "Yes, even if I have to pay" = "Yes")) %>%
  dplyr::select(
    study, age, gender, educ, take_vaccine, 
    starts_with("trust_vaccine_"), weight = pweight, cluster = slum_code) %>%
  dplyr::mutate(across(c(starts_with("trust_vaccine"), weight), ~ replace(., is.na(.), 0)))

@@

npl <- 
  read.dta13("1_country_data/npl/vaccines_nepal.dta") %>%
  dplyr::as_tibble() %>% 
  dplyr::rename(
    take_vaccine = if_vaccine_take,
    weight = wt_s) %>%
  dplyr::mutate(
    gender = ifelse(resp_female == 1, "Female", "Male"),
    educ = recode(educ, 
                  "0" = "Less than secondary",
                  "1" = "Less than secondary",
                  "2" = "Less than secondary",
                  "3" = "Secondary",
                  "4" = "Secondary",
                  "5" = "Secondary",
                  "6" = "More than secondary",
                  "7" = "More than secondary"),
    across(matches(c("reason_take", "reason_not_take")), 
           ~ recode(., "Selected" = 1, "Not selected" = 0, .default = NaN))) %>%
  dplyr::rename(
    yes_vaccine_1 = reason_take_vaccine1,
    yes_vaccine_2 = reason_take_vaccine3,
    yes_vaccine_3 = reason_take_vaccine4,
    yes_vaccine_4 = reason_take_vaccine5,
    yes_vaccine_5 = reason_take_vaccine6,
    yes_vaccine_666 = reason_take_vaccine9,
    no_vaccine_1 = reason_not_take1,
    no_vaccine_2 = reason_not_take2,
    no_vaccine_3 = reason_not_take3,
    no_vaccine_4 = reason_not_take4,
    no_vaccine_5 = reason_not_take5,
    no_vaccine_6 = reason_not_take6,
    no_vaccine_7 = reason_not_take7,
    no_vaccine_8 = reason_not_take8,
    no_vaccine_9 = reason_not_take9,
    no_vaccine_666 = reason_not_take10) %>%
  dplyr::mutate(
    yes_vaccine_1 = 
      ifelse(reason_take_vaccine2 == 1, 1, yes_vaccine_1),
    yes_vaccine_666 = 
      ifelse(reason_take_vaccine7 == 1, 1, yes_vaccine_666),
    yes_vaccine_666 = 
      ifelse(reason_take_vaccine8 == 1, 1, yes_vaccine_666),
    vaccine_safe = 
      ifelse(vacc_safe == "Somewhat agree" | vacc_safe == "Strongly agree",1,0),
    vaccine_effective = 
      ifelse(vacc_effective == "Somewhat agree" | vacc_effective == "Strongly agree",1,0),
    trust_vaccine_1 = 
      ifelse(trust_vaccine == "Family members", 1, 0),
    trust_vaccine_2 = 
      ifelse(trust_vaccine == "Friends you see and talk to", 1, 0),
    trust_vaccine_3 = 
      ifelse(trust_vaccine == "Religious leaders", 1, 0),
    trust_vaccine_4 = 
      ifelse(trust_vaccine == "Famous person", 1, 0),
    trust_vaccine_5 = 
      ifelse(trust_vaccine == "Doctors or other staff at a community health clinic", 1, 0),
    trust_vaccine_6 = 
      ifelse(trust_vaccine == "Advice of the national health service", 1, 0),
    trust_vaccine_7 = 
      ifelse(trust_vaccine == "Traditional healers", 1, 0),
    trust_vaccine_8 = 
      ifelse(trust_vaccine == "Traditional media (newspaper, radio)", 1, 0),
    trust_vaccine_9 = 
      ifelse(trust_vaccine == "Online medical discussion groups", 1, 0),
    trust_vaccine_dk = 
      ifelse(trust_vaccine == "DNK", 1, 0),
    trust_vaccine_refuse = 
      ifelse(trust_vaccine == "Refused", 1, 0),
    trust_vaccine_nr = 
      ifelse(is.na(trust_vaccine), 1, 0),
    trust_vaccine_other = 
      ifelse(trust_vaccine == "Advice of the WHO", 1, 0),
    trust_vaccine_666 = 
      ifelse(trust_vaccine == "None of these/Someone else- specify", 1, 0),
    study = "npl_yale") %>%
  dplyr::select(
    study, age, gender, -educ, take_vaccine, 
    starts_with(c("yes_vaccine", "no_vaccine", "trust_vaccine_")), 
    vaccine_safe, vaccine_effective, weight, cluster = Village_Code, -no_vaccine_8) %>%
  dplyr::mutate(across(c(yes_vaccine_1:trust_vaccine_666), ~replace(., is.na(.), 0)))

@@

vars <- readxl::read_excel("dictionary.xlsx") %>% pull(outcome)

df <- 
  dfs %>% 
  plyr::llply(
    .data = .,
    .fun = function(df) {
      if (!is.null(df$cluster)) df %<>% mutate(cluster = as.character(cluster))
      return(df)
    }
  ) %>% 
  dplyr::bind_rows() %>% 
  dplyr::left_join(dplyr::select(studies, study, country), by = "study") %>%
  dplyr::mutate(
    take_vaccine_num = ifelse(take_vaccine == "Yes", 1, 0),
    take_vaccine_num = ifelse(is.na(take_vaccine), 0, take_vaccine_num),
    cluster = 
      ifelse(is.na(cluster), NA, 
             paste0(gsub(pattern = " ", replacement = "_", x = tolower(country)), "_", cluster))) %>%
  dplyr::select(any_of(vars))

>>>>

ind <-
  read.dta13("1_country_data/ind/IGC_vacstudy_blfu12.dta", 
             nonint.factors = TRUE) %>%
  dplyr::as_tibble() %>% 
  dplyr::filter(!is.na(vac1)) %>% 
  dplyr::rename(
    age = HH_age,
    gender = HH_sex,
    take_vaccine = vac1) %>%
  dplyr::mutate(
    w_id=paste0(slum_code, hhid),
    study = "ind_igc",
    educ = ifelse(hhb_hh_head_educs == 1, "More than secondary", NA_character_),
    educ = ifelse(hhb_hh_head_educs == 0, "Less than secondary", educ),
    gender = as.factor(gender),
    gender = recode(gender, 
                    "1" = "Male", 
                    "0" = "Female"), 
    take_vaccine = recode(take_vaccine, 
                          "Yes, only for free" = "Yes", 
                          "Yes, even if I have to pay" = "Yes")) %>%
  dplyr::select(w_id, survey_date,
                study, age, gender, educ, take_vaccine, 
                starts_with("trust_vaccine_"), weight = pweight, cluster = slum_code) %>%
  dplyr::mutate(across(c(starts_with("trust_vaccine"), weight), ~ replace(., is.na(.), 0)))

ind_avg <- ind %>%
  dplyr::mutate(
    take_vaccine_num = ifelse(take_vaccine == "Yes", 1, 0),
    take_vaccine_num = ifelse(is.na(take_vaccine), 0, take_vaccine_num)) %>%
  group_by(w_id) %>%
  summarise(mean = mean(take_vaccine_num))

ind <- ind %>%
  mutate(date=lubridate::mdy(survey_date)) %>%
  group_by(w_id) %>%
  slice(which.max(date)) %>%
  left_join(ind_avg)

@@

npl <- 
  read.dta13("1_country_data/npl/vaccines_nepal.dta") %>%
  dplyr::as_tibble() %>% 
  dplyr::rename(
    take_vaccine = if_vaccine_take,
    weight = wt_s) %>%
  dplyr::mutate(
    gender = ifelse(resp_female == 1, "Female", "Male"),
    educ = recode(educ, 
                  "0" = "Less than secondary",
                  "1" = "Less than secondary",
                  "2" = "Less than secondary",
                  "3" = "Secondary",
                  "4" = "Secondary",
                  "5" = "Secondary",
                  "6" = "More than secondary",
                  "7" = "More than secondary"),
    across(matches(c("reason_take", "reason_not_take")), 
           ~ recode(., "Selected" = 1, "Not selected" = 0, .default = NaN))) %>%
  dplyr::rename(
    yes_vaccine_1 = reason_take_vaccine1,
    yes_vaccine_2 = reason_take_vaccine3,
    yes_vaccine_3 = reason_take_vaccine4,
    yes_vaccine_4 = reason_take_vaccine5,
    yes_vaccine_5 = reason_take_vaccine6,
    yes_vaccine_666 = reason_take_vaccine9,
    no_vaccine_1 = reason_not_take1,
    no_vaccine_2 = reason_not_take2,
    no_vaccine_3 = reason_not_take3,
    no_vaccine_4 = reason_not_take4,
    no_vaccine_5 = reason_not_take5,
    no_vaccine_6 = reason_not_take6,
    no_vaccine_7 = reason_not_take7,
    no_vaccine_8 = reason_not_take8,
    no_vaccine_9 = reason_not_take9,
    no_vaccine_666 = reason_not_take10) %>%
  dplyr::mutate(
    yes_vaccine_1 = 
      ifelse(reason_take_vaccine2 == 1, 1, yes_vaccine_1),
    yes_vaccine_666 = 
      ifelse(reason_take_vaccine7 == 1, 1, yes_vaccine_666),
    yes_vaccine_666 = 
      ifelse(reason_take_vaccine8 == 1, 1, yes_vaccine_666),
    vaccine_safe = 
      ifelse(vacc_safe == "Somewhat agree" | vacc_safe == "Strongly agree",1,0),
    vaccine_effective = 
      ifelse(vacc_effective == "Somewhat agree" | vacc_effective == "Strongly agree",1,0),
    trust_vaccine_1 = 
      ifelse(trust_vaccine == "Family members", 1, 0),
    trust_vaccine_2 = 
      ifelse(trust_vaccine == "Friends you see and talk to", 1, 0),
    trust_vaccine_3 = 
      ifelse(trust_vaccine == "Religious leaders", 1, 0),
    trust_vaccine_4 = 
      ifelse(trust_vaccine == "Famous person", 1, 0),
    trust_vaccine_5 = 
      ifelse(trust_vaccine == "Doctors or other staff at a community health clinic", 1, 0),
    trust_vaccine_6 = 
      ifelse(trust_vaccine == "Advice of the national health service", 1, 0),
    trust_vaccine_7 = 
      ifelse(trust_vaccine == "Traditional healers", 1, 0),
    trust_vaccine_8 = 
      ifelse(trust_vaccine == "Traditional media (newspaper, radio)", 1, 0),
    trust_vaccine_9 = 
      ifelse(trust_vaccine == "Online medical discussion groups", 1, 0),
    trust_vaccine_dk = 
      ifelse(trust_vaccine == "DNK", 1, 0),
    trust_vaccine_refuse = 
      ifelse(trust_vaccine == "Refused", 1, 0),
    trust_vaccine_nr = 
      ifelse(is.na(trust_vaccine), 1, 0),
    trust_vaccine_other = 
      ifelse(trust_vaccine == "Advice of the WHO", 1, 0),
    trust_vaccine_666 = 
      ifelse(trust_vaccine == "None of these/Someone else- specify", 1, 0),
    study = "npl_yale") %>%
  dplyr::select(
    study, age, gender, -educ, take_vaccine, trust_vaccine, 
    starts_with(c("yes_vaccine", "no_vaccine", "trust_vaccine_")), 
    vaccine_safe, vaccine_effective, weight, cluster = Village_Code, -no_vaccine_8) %>%
  dplyr::mutate(across(c(yes_vaccine_1:trust_vaccine_666), ~replace(., is.na(.), 0)))

@@

vars <- readxl::read_excel("2_input_data/dictionary.xlsx") %>% pull(outcome)

df <- 
  dfs %>% 
  plyr::llply(
    .data = .,
    .fun = function(df) {
      if (!is.null(df$cluster)) df %<>% mutate(cluster = as.character(cluster))
      return(df)
    }
  ) %>% 
  dplyr::bind_rows() %>% 
  dplyr::left_join(dplyr::select(studies, study, country), by = "study") %>%
  dplyr::mutate(
    take_vaccine_num = ifelse(take_vaccine == "Yes", 1, 0),
    take_vaccine_num = ifelse(is.na(take_vaccine), 0, take_vaccine_num),
    take_vaccine_num = ifelse(study=="ind_igc", mean, take_vaccine_num),
    cluster = 
      ifelse(is.na(cluster), NA, 
             paste0(gsub(pattern = " ", replacement = "_", x = tolower(country)), "_", cluster))) %>%
  dplyr::select(any_of(vars))
